Comprehensive study of the global phase diagram of the $J$-$K$-$\Gamma$ model on a triangular lattice

### 2021-01-24 paper/paper.tex
Paper 2021-01-24 14:04

\added[swang]{Although the singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ show that there are phase transitions between stripe-A, stripe-B and stripe-C (see Appendix \ref{apx:PhaseBoundary} for details), the differences between these phases cannot be seen from the SSFs, which show the same characteristic wave vector [Fig.~\ref{fig:StructureFactors}(a), (b), (c) and (d)]. In fact, the most commonly used physcial quantity to distinguish different quantum phases is the order parameter. For the magnetically ordered phases, such as the stripe phases discussed here, the order parameter can be defined as $\bm{m}(\bm{Q})=\frac{1}{N} \sum_{i} \langle \Omega | \bm{S}_{i} | \Omega \rangle e^{i\bm{Q} \cdot \bm{r}_{i}}$, where $|\Omega\rangle$ is the ground state and $\bm{Q}$ is the characteristic wave vector. Thus, both the ordering vector and the moment direction are the defining characteristic. The difference between the stripe-A, stripe-B and stripe-C phases lies in that they have different moment directions, which we will discuss in detail later in the paper.}

@@

\added[swang]{
\section{\label{apx:SizeEffect}The effects of system size on the phase boundaries}
To study the effects of system size on the zero-temperature quantum phase diagram, we also carry out ED calculations on a $2 \times 6$ cluster with periodic boundary condition, see Fig.~\ref{fig:SecondDerivatives26}(g) for the shape of the cluster as well as the form of the boundary condition. This cluster and the boundary condition are compatible with most of the magnetic orders, such as FM, stripe, 120$^\circ$ N\'{e}el, dual N\'{e}el and six-chain modulated stripe shown in Fig.~\ref{fig:ModulatedStripe}(a).

In Fig.~\ref{fig:SecondDerivatives26}(a)-(c), the $\alpha$ parameter is fixed to $0.05\pi$, $0.2\pi$ and $0.75\pi$, respectively. In Fig.~\ref{fig:SecondDerivatives26}(d)-(f), the $\beta$ parameter is fixed to 0, $0.5\pi$ and $1.5\pi$, respectively. The singularities in Fig.~\ref{fig:SecondDerivatives26}(a)-(f) are consistent with the results of the $4 \times 6$ cluster shown in Fig.~\ref{fig:SecondDerivatives46}(a)-(f) even though the positions of the phase boundaries are slightly shifted. It is worth to note that, in Fig.~\ref{fig:SecondDerivatives26}(b) the $\beta$ parameter is fixed to $0.2\pi$ while in Fig.~\ref{fig:SecondDerivatives46}(b) $\beta = 0.3\pi$, since the region of the 120$^\circ$ N\'eel phase extends to a larger area for the $2 \times 6$ cluster, which leads to that $\beta = 0.3\pi$ is still in the 120$^\circ$ N\'eel phase. Thus, in comparison with the results for the $4 \times 6$ cluster, we find that different system sizes do not change the phase diagram qualitatively and only affect the locations of the phase boundaries.

>>>>

\added[swang]{Although the singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ show that there are phase transitions between stripe-A, stripe-B and stripe-C (see Appendix \ref{apx:PhaseBoundary} for details), the differences between these phases cannot be seen from the SSFs, which show the same characteristic wave vector [Fig.~\ref{fig:StructureFactors}(a), (b), (c) and (d)]. In fact, the most commonly used physcial quantity to distinguish different quantum phases is the order parameter. For the magnetically ordered phases, such as the stripe phases discussed here, the order parameter can be defined as $\bm{m}(\bm{Q})=\frac{1}{N} \sum_{i} \langle \Omega | \bm{S}_{i} | \Omega \rangle e^{i\bm{Q} \cdot \bm{r}_{i}}$, where $|\Omega\rangle$ is the ground state and $\bm{Q}$ is the characteristic wave vector. Thus, both the ordering vector and the moment direction are the defining characteristics. The difference between the stripe-A, stripe-B and stripe-C phases lies in that they have different moment directions, which we will discuss in detail later.}

@@

\added[swang]{
\section{\label{apx:SizeEffect}Effects of system size on the phase boundaries}
To study the effects of system size on the zero-temperature quantum phase diagram, we also carry out ED calculations on a $2 \times 6$ cluster with periodic boundary condition, see Fig.~\ref{fig:SecondDerivatives26}(g) for the shape of the cluster as well as the form of the boundary condition. This cluster and the boundary condition are compatible with most of the magnetic orders, such as FM, stripe, 120$^\circ$ N\'{e}el, dual N\'{e}el and six-chain modulated stripe shown in Fig.~\ref{fig:ModulatedStripe}(a).

In Fig.~\ref{fig:SecondDerivatives26}(a)-(c), the $\alpha$ parameter is fixed to be $0.05\pi$, $0.2\pi$ and $0.75\pi$, respectively. In Fig.~\ref{fig:SecondDerivatives26}(d)-(f), the $\beta$ parameter is fixed to be 0, $0.5\pi$ and $1.5\pi$, respectively. The singularities in Fig.~\ref{fig:SecondDerivatives26}(a)-(f) are consistent with the results of the $4 \times 6$ cluster shown in Fig.~\ref{fig:SecondDerivatives46}(a)-(f) even though the positions of the phase boundaries are slightly shifted. It is worth to note that, in Fig.~\ref{fig:SecondDerivatives26}(b) the $\beta$ parameter is fixed to $0.2\pi$ while in Fig.~\ref{fig:SecondDerivatives46}(b) $\beta = 0.3\pi$, since the region of the 120$^\circ$ N\'eel phase extends to a larger area for the $2 \times 6$ cluster, which leads to that $\beta = 0.3\pi$ is still in the 120$^\circ$ N\'eel phase. Thus, in comparison with the results for the $4 \times 6$ cluster, we find that different system sizes do not change the phase diagram qualitatively and only affect the locations of the phase boundaries.
